MINOS Handover Plots

### 2024-10-03 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Tweaks to income module and additions to plotting scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

# data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
# data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))
# 
# nrow(data)
# 
# 
# 5463300
# 
# 4580000
# 
# 
# 359328 / 458000 * 100
# 
# 100 / 78.4559
# 
# 
# 109338 * 12.74601

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_33_scot_clipped/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

data <- do.call(rbind, generate_df_list('whole_pop', 'baseline'))
data.fam <- do.call(rbind, generate_df_list('families', 'baseline'))

nrow(data)

5463300

4580000

359328 / 458000 * 100

100 / 78.4559

359328 * 12.74601

#2030	-1800.26

print('RESULT 1:')
1800.26 * 12.74601

109338 / 1262147 * 100

100 / 86.62906

109338 * 11.5437

# 2030	-590.55

print('RESULT 2:')
590.55 * 11.5437

### 2024-10-03 minos/validation/handovers.Rmd
Tweaks to income module and additions to plotting scripts

ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

>>>>

ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')

rm(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
```
